Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-07 draft.tex
complete description of game in sec:structure

\subsection{Timing and Structure of Interaction}

@@

The payoff functions and all parameters, including probabilities in the war lottery, are common knowledge for all players, and actions are immediately observed by all players at the time they occur. There are an infinite number of periods $t=1,2,\ldots$, with play proceeding until an absorbing state is reached.

@@

The strategies for the government and secessionists in this equilibrium are to play their best responses in the stage game given the continuation values induced by the investments of the outside actors. Unless otherwise noted below, playing Status Quo is the best response for both inside actors. The strategies for the insides actors are the the following, organized according to the patron's investments in each state variable. In period $t$:

>>>>

\subsection{Timing and Structure of Interaction}
\label{sec:structure}

@@

The payoff functions and all parameters, including probabilities in the war lottery, are common knowledge for all players, and actions are immediately observed by all players at the time they occur. There are an infinite number of periods $t=1,2,\ldots$, with play proceeding until an absorbing state is reached. This is a dynamic game because the fundamentals determining the payoffs of the inside actors are state variables whose values persist from period to period and in which the outside actors can make investments.

@@

The strategies for the government and secessionists in this equilibrium are to play their best responses in the stage game given the continuation values induced by the investments of the outside actors. Unless otherwise noted below, playing Status Quo is the best response for both inside actors. The strategies for the insides actors are the following, organized according to the patron's investments in each state variable. In period $t$:
